Difference Scores: Paired Samples T-test

### 2024-03-19 examples/1a_Examples_DifferenceScores_PairedTtests.qmd
updates
test

<p>

This example assesses growth in a subsample of ABCD participants from Baseline (T0) to the 1-Year follow-up (T1), using weight as a representative metric. The analysis is conducted in two primary steps: 1) a difference score is calculated between baseline and Year_1 weight measurements for each participant; 2) a one-sample t-test is used to test whether the difference score is statistically different than a null hypothesis of zero change. Finally, a visual inspection is further conducted via a scatterplot to graphically represent the relationship between participant's weight at Baseline and Year_1. The ensuing analysis and interpretations are detailed in the subsequent sections.

@@

df <- my_data

>>>>

<p>
test-remove
This example assesses growth in a subsample of ABCD participants from Baseline (T0) to the 1-Year follow-up (T1), using weight as a representative metric. The analysis is conducted in two primary steps: 1) a difference score is calculated between baseline and Year_1 weight measurements for each participant; 2) a one-sample t-test is used to test whether the difference score is statistically different than a null hypothesis of zero change. Finally, a visual inspection is further conducted via a scatterplot to graphically represent the relationship between participant's weight at Baseline and Year_1. The ensuing analysis and interpretations are detailed in the subsequent sections.

@@
